### 2014-04-29 ApTranscriptome_TR.Rmd
Minor changes

Note that I used the reduced assembly, prior to cleaning out contaminants. Rather than re-running this, I remove contaminants by ...

@@

```{r fdr}
RxNpval$padj <- p.adjust(RxNpval$pval, method = "fdr")
# Plot FDR values against initial pvalues
par(mfrow = c(2,1))
hist(RxNpval$pval)
hist(RxNpval$padj)

@@

```

>>>>

Note that I used the reduced assembly, prior to cleaning out contaminants. As I use the "clean" assembly for read mapping and identification of responsive genes, the contaminants are dis-regarded in downstream analyses.

@@

```{r padjust}
RxNpval$padj <- p.adjust(RxNpval$pval, method = "fdr")
# Plot FDR values against initial pvalues
par(mfrow = c(2,1))
hist(RxNpval$pval)
hist(RxNpval$padj)

@@
